Finding a closest point in a lattice of Voronoi's first kind

### 2014-07-13 reviews/response.tex

``Our results can be placed in the context of a modification of the closest lattice point problem called the \emph{closest vector problem with preprocessing}~\cite{micciancio_hardness_2001,feige_inapproximability_2004,Regev_2004_inappox_lattice_with_preprocessing,Aleknovish_hardness_with_preprocessing_2011,knot_hardness_cvvp_2014,Dadush_cvp_with_distance_guarantee_2014}.  In this problem some ``advice'' of polynomial size about the lattice is assumed to be given.  The advice might come in the form of a particular basis for the lattice or might take other forms.  The advice may be used to compute a closest lattice point, hopefully with reduced complexity.  %Even this modification of the closest lattice point problem is known to be NP-hard~\cite{micciancio_hardness_2001,feige_inapproximability_2004}.  
Our algorithm can be viewed as an efficient solution for the closest vector problem with preprocessing for the lattices of Voronoi's first kind.  The advice given is the obtuse superbasis.''

\item\textbf{Comment:} 
Hence, from the standpoint of CVPP, the algorithm in this paper gives essentially the first
exact polynomial time algorithm over a reasonably large and natural class of lattices, i.e. those
of Voronoi's first kind. Lastly, removing the need for preprocessing for these lattices, at least for
solving SVP without being given an obtuse superbasis, would require a substantial breakthrough
in the theory of lattice problems (not stated in paper). Indeed, by a simple reduction this would
allow us to decide whether a lattice (given any of its bases) is a rotation of $\ints^n$ (which is clearly
of Voronoi's first kind). This is a long standing open problem in the theory of lattices, which has
only recently been solved in certain very special cases~[6].
\\\textbf{Response:}
The final paragraph of Section~\zref{sec:discussion} has been modified to make the connection with the existing problem of determining whether a rectangular basis exists in a given lattice.

``A final remark is that our algorithm assumes that the obtuse superbasis is known in advance.  It is known that all lattices of dimension less than or equal to 3 are of Voronoi's first kind and an algorithm exists to recover the obtuse superbasis in this case~\cite{SPLAG}.  Lattices of dimension larger than 3 need not be of Voronoi's first kind.  Given a lattice, is it possible to efficiently decide whether it is of Voronoi's first kind?  Is it possible to efficiently find an obtuse superbasis if it exists?  It is suspected that the answer to this second question is no because an efficient solution would yield a solution to a known problem, that of determining whether a lattice is rectangular (has a basis consisting of pairwise orthogonal vectors) given an arbitrary basis~\cite{Lenstra_Silverberg_revisting_gentra_szydlo_2014}.''  %It is suspected that this simpler problem is difficult.''

### 2014-07-13 paper.tex
minor edits in response to Vaughan

A final remark is that our algorithm assumes that the obtuse superbasis is known in advance.  It is known that all lattices of dimension less than or equal to 3 are of Voronoi's first kind and an algorithm exists to recover the obtuse superbasis in this case~\cite{SPLAG}.  Lattices of dimension larger than 3 need not be of Voronoi's first kind.  An interesting question is: given a lattice, is it possible to efficiently decide whether it is of Voronoi's first kind?  A related question is: is it possible to efficiently find an obtuse superbasis if it exists?  It is suspected that the answer to this second question is no.  An efficient solution would yield a solution to a known problem, that of determining whether a lattice is rectangular (has a basis consisting of pairwise orthogonal vectors) given an arbitrary basis~\cite{Lenstra_Silverberg_revisting_gentra_szydlo_2014}.  It is suspected that this simpler problem is difficult.

>>>>

A final remark is that our algorithm assumes that the obtuse superbasis is known in advance.  It is known that all lattices of dimension less than or equal to 3 are of Voronoi's first kind and an algorithm exists to recover the obtuse superbasis in this case~\cite{SPLAG}.  Lattices of dimension larger than 3 need not be of Voronoi's first kind.  Given a lattice, is it possible to efficiently decide whether it is of Voronoi's first kind?  Is it possible to efficiently find an obtuse superbasis if it exists?  It is suspected that the answer to this second question is no because an efficient solution would yield a solution to a known problem, that of determining whether a lattice is rectangular (has a basis consisting of pairwise orthogonal vectors) given an arbitrary basis~\cite{Lenstra_Silverberg_revisting_gentra_szydlo_2014}.  %It is suspected that this simpler problem is difficult.
